---
title: 'CPDA SP18 Assignment #1'
output:
  html_notebook: default
  html_document: default
  pdf_document: default
---
```{r}
install.packages("matlab")
library("matlab")
```

Consider the following Matrix:
```{r}
A <- matrix(c(8,-1,2,-1,2,-2,2,-2,3),3,3,byrow = TRUE)
print(A)
```
### a)Compute the determinant and rank of the Matrix A.  What can you say about the rank of the matrix from the determinant?
```{r}
det(A)
qr(A)$rank
```
Since the determinant(13) is not zero, we know the matrix is not sigular. In this case, A has full rank.  We can confirm rank by putting A in reduced row echelon form, showing 3 non-zero pivots.
```{r}
library(pracma)
rref(A)
```

### b) Write a code to calculate the eigenvalue-eigenvector pairs of the matrix A.

```{r}
A.eigen <- eigen(A)
A.eigen
```
### c) Calculate the angle between the eigenvectors corresponding to the two largest eigenvalue in degrees. (2 points)
```{r}
degs<-function(rads) {
  round(rads*180/pi, digits = 0)
}
theta <- function(v1, v2){
  degs(acos(dot(v1, v2) / (sqrt(sum(v1^2)) * sqrt(sum(v2^2)))))
}
theta(A.eigen$vectors[,1], A.eigen$vectors[,2])
```

### d) Is the matrix A positive definite? (2 points)
```{r}
install.packages("matrixcalc")
library("matrixcalc")
A.eigen
is.positive.definite(A)
```


All the eigen$values are > 0, so A is positive-definite.

### e) Let T  be the matrix constructed by stacking the eigenvectors of A as its columns. Calculate T−1 A T . (2 points)
```{r}
calculation.e <- function(v, t){
  tinv <- inv(t)
  prd <- t(tinv) %*% v
  t(prd) %*% t
}

calculation.e(A, A.eigen$vectors)

```
### f) Find the trace of the matrix A. (2 points)
By definition, the trace is the sum of the diagonals.
```{r}
sum(diag(A))
```
### g) Find A^2 . (2 points)
A^2 is also A dot A
```{r}
A %*% A
```


