---
title: 'CPDA SP18 Assignment #1'
output:
  pdf_document: default
  html_notebook: default
---
Consider the following Matrix:
```{r}
A <- matrix(c(8,-1,2,-1,2,-2,2,-2,3),3,3,byrow = TRUE)
print(A)
```
### a)Compute the determinant and rank of the Matrix A.  What can you say about the rank of the matrix from the determinant?
```{r}
det(A)
qr(A)$rank
```
Since the determinant(13) is not zero, we know the matrix is not sigular. In this case, A has full rank.  We can confirm rank by putting A in reduced row echelon form, showing 3 non-zero pivots.
```{r}
library(pracma)
rref(A)
```

### b) Write a code to calculate the eigenvalue-eigenvector pairs of the matrix A.

```{r}
A.eigen <- eigen(A)
A.eigen
```
### c) Calculate the angle between the eigenvectors corresponding to the two largest eigenvalue in degrees. (2 points)
```{r}
degs<-function(rads) {
  round(rads*180/pi, digits = 0)
}
theta <- function(v1, v2){
  degs(acos(dot(v1, v2) / (sqrt(sum(v1^2)) * sqrt(sum(v2^2)))))
}
theta(A[,1], A[,2])
```

