---
title: "CPDA SP18 Assignment 2"
author: "Hugh Jamieson(jamieson.65)"
output:
  pdf_document: default
  html_notebook: default
---
## Introduction
A management firm wants to buy a house from a landlord. The firm wants to estimate an appropriate price of the house that they can offer to the landlord. They hire you as a machine learning engineer to do the job. You have to make an estimation based on the total land area in square feet.

## (a) Import the dataset and plot.
```{r}
housing.data<-read.csv("/Users/hughj/Development/osu/machine-learning/osu-mach-learn/module-2/HousingData.txt", 
   header=FALSE,
   sep = ",",
   col.names = c("area","cost"))

# plot the original input dataset
plot(housing.data$area,housing.data$cost,type="p" ,
     main = "Housing Dataset", 
     xlab="area in 100 sqft",
     ylab="price in 100K")
```
## (b) Use linear least squares to find the optimal values of theta (0ls).
```{r}
# create the matrix for A
rows <- nrow(housing.data)
A <- as.matrix(cbind(rep(1,rows), housing.data$area))
b <- as.matrix(housing.data$cost)
# calculate the optimal values of theta:
theta <- solve(t(A)%*%A)%*%t(A) %*% b
b0 <- theta[1]
b1 <- theta[2]
# print beta0 & beta1
cat("intercept: ",b0,"\n")  
cat("slope:" ,b1, "\n")
```
## (c) Plot the hypothesis function f(x) with the data:
```{r}
plot(housing.data$area,housing.data$cost,type="p" ,
     main = "Housing Dataset", 
     xlab="area in 100 sqft",
     ylab="price in 100K")
abline(b0, b1, col=3)
```
## (d) Find the estimated price of a house in dollars for 700 sqft home:
```{r}
area <- 7
price <- (b1 * area + b0) * 10^5
cat("Estimated price of 700 sqft home: $",price, "\n")
```

